Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-22 Cover_letter_JPM.tex
Bayes for Answer 2.5

@@

%Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
***We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors. The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.

@@

***  a gene signature with deep learning CNN,
or http://gepia2.cancer-pku.cn/#index
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
or
% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.

or \cite{Zhao2018}
Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/

@@

*** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

@@

***Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these primitive biomarkers. In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.

** or using %Rplot_GSE65858_CoxHR1.5_top19.pdf
KM estimate and Cox modeling to yield a geographically closed gene cluster:
CAMK2N1, TIMM10, TNFAIP6, SPP1, ADAMTSL2.

>>>>

\usepackage{subcaption} % for figure  side by side

@@

***The RLassoCox\cite{Liu2021} (bioconductor package, available at https://github.com/weiliu123/RLassoCox) trains the RLasso-Cox model based on gene expression profiles, survival information and gene interaction networks.
It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes. The RLasso-Cox model uses random walk to evaluate the topological weight of genes, and then highlights topologically important genes to identify survival biomarkers for HNSCC.
dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.

%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
RLassoCox\\
We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors. The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.

% **** [2021/06/22] by Bayes_survival.R
The results shows
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
cv.mod.candidate 62 genes are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

\begin{figure}[!tbp]
%     % two PDF side by side \usepackage{subcaption}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
        \caption{TCGA HNSCC cohort}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
       \caption{GSE65858 HNSCC cohort}
  \end{subfigure}
  \caption{side by side}
  \label{fig:Bayes62}
\end{figure}

@@

%***  a gene signature with deep learning CNN,
%or http://gepia2.cancer-pku.cn/#index
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
%or
% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.

%or \cite{Zhao2018} Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/

@@

%*** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

@@

%***Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these primitive biomarkers. In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.

%** or using %Rplot_GSE65858_CoxHR1.5_top19.pdf
%KM estimate and Cox modeling to yield a geographically closed gene cluster:
%CAMK2N1, TIMM10, TNFAIP6, SPP1, ADAMTSL2.
